---
title: "Assessment: Performance metrics for normScore in benchmarking datasets"
author: 
- name: "Julia García Currás"
  affiliation: "julia.garcia@biostatech.com"
date: "`r Sys.Date()`"
output: 
  # rmarkdown::html_document:
  #   theme:
  #     version: 5
  #     bootswatch: flatly
  # prettydoc::html_pretty:
  #   theme: cayman
  #   toc: yes
  #   self_contained: yes
  rmdformats::readthedown:
    # toc: yes
    self_contained: yes
    css: ./Complementos/cambios.css
    includes:
      in_header: "./Complementos/favicon.html"
      after_body: ./Complementos/footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  eval = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  include = TRUE,
  results = 'asis'
)

library(dplyr)
library(DT)
library(ggplot2)
library(ggpubr)

# Color:
# "#3d1308" = "#6C8092"
# "#9F2042" = "#003C72"
# "#c7254e"
#"#d64a70"
```

```{r}
# variables
inputDir <- "C:/Users/julia/Documents/GitHub/normScore-development/Benchmarking/Data/"
# outDir <- "C:/Users/julia/Documents/GitHub/normScore/goldStandard/ProcessedDatasets/"
js <- c(
"function(row, data, num, index){",
"  var $row = $(row);",
"  if($row.hasClass('even')){",
"    $row.css('background-color', 'white');",
"    $row.hover(function(){",
"      $(this).css('background-color', 'lightgrey');",
"     }, function(){",
"      $(this).css('background-color', 'white');",
"     }",
"    );",  
"  }else{",
"    $row.css('background-color', '#EDFDFA');",
"    $row.hover(function(){",
"      $(this).css('background-color', 'lightgrey');",
"     }, function(){",
"      $(this).css('background-color', '#EDFDFA');",
"     }",
"    );",  
"  }",
"}"  
)
```

```{r}
source(file = "../goldStandard/3_AssessmentFunctions.R")
```


# DIA datasets

```{r}
# LOADING DATA FOR DIA
tipoAnalisis <- "DIA"
resNormScore <- readRDS(file = paste0(inputDir, tipoAnalisis, "/", tipoAnalisis, "_normScoreRanking.rds"))
datosEval <- readRDS(file = paste0(inputDir, tipoAnalisis, "/3_EvalData_3_MAPE.rds"))
```


```{r}
# PREPARING DATA
### MAPE ####
mapeRealRank <- list()
for (nombre in names(datosEval)){
  lista <- datosEval[[nombre]]
  lista[["MAD"]] <- NULL
  resInd <- sapply(lista, "[[", 7)
  resInd <- sort(resInd)
  resInd[names(resInd)] <- 1:8
  mapeRealRank[[nombre]] <- resInd # Real classification
}

# normScore rank order by real accuracy order
normScoreRank <- list()
for (nombre in names(resNormScore)){
  # orden real por MAPE
  realOrden <- names(mapeRealRank[[nombre]])
  
  # Orden por normScore
  resInd <- resNormScore[[nombre]]
  resInd <- sort(resInd)
  resInd[names(resInd)] <- 1:8
  
  # Ordenar según ranking real
  resInd <- resInd[realOrden]
  
  # Out
  normScoreRank[[nombre]] <- resInd
}


# Kendall correlation
corRes <- sapply(names(mapeRealRank), function(i) cor(
  x = unname(mapeRealRank[[i]]), 
  y = unname(normScoreRank[[i]]),
  method = "kendall"), USE.NAMES = T, simplify = F)
```

```{r}

resNormScoreNames <- lapply(resNormScore, names)
mapeRealRankNames <- lapply(mapeRealRank, names)


### Global ####
# Non corrected
summaryGlobal <- resultsGlobal(
  resGlobalNS = resNormScoreNames, 
  resGlobalGS_BEST = lapply(mapeRealRankNames, function(i) i[1]),
  resGlobalGS_BESTS = lapply(mapeRealRankNames, function(i) i[1:3]), 
  resGlobalGS_WORST = NULL
  )
```

### Best methods (top) {.tabset}

#### Top 1 - only the best method {-}

```{r}
summaryGlobal$Best$hitTable
```

#### Top 1 - all best methods {-}

```{r}
summaryGlobal$Bests$hitTable
```


#### MRR - only the best method {-}

```{r}
# allClassess <- rev(sort(unique(df$Pos)))
allClassess <- 1/1:8
df <- data.frame(Pos = summaryGlobal$Best$mrrRes)
df$Position <- factor(
  df$Pos, 
  levels = allClassess, 
  # levels = rev(sort(unique(df$Pos))), 
  labels = paste0("Posición ", 1:8))
Biostatech::getCatTable(df$Position)$tablaFormato
```

#### MRR - all best methods {-}

```{r}
df <- data.frame(Pos = summaryGlobal$Bests$mrrRes)
df$Position <- factor(
  df$Pos, 
  levels = allClassess, 
  labels = paste0("Posición ", 1:8))
Biostatech::getCatTable(df$Position)$tablaFormato
```

#### MRR bottom - all best methods {-}

La posición más baja de la mejor normalización del grupo determinado por MAPE.  

```{r}
df <- data.frame(Pos = summaryGlobal$Bests$mrrResBottom)
df$Position <- factor(
  df$Pos, 
  levels = allClassess, 
  labels = paste0("Posición ", 1:8))
Biostatech::getCatTable(df$Position)$tablaFormato
```



# DDA datasets

```{r}
# LOADING DATA FOR DIA
tipoAnalisis <- "DDA"
resNormScore <- readRDS(file = paste0(inputDir, tipoAnalisis, "/", tipoAnalisis, "_normScoreRanking.rds"))
datosEval <- readRDS(file = paste0(inputDir, tipoAnalisis, "/3_EvalData_3_MAPE.rds"))
```


```{r}
# PREPARING DATA
### MAPE ####
mapeRealRank <- list()
for (nombre in names(datosEval)){
  lista <- datosEval[[nombre]]
  lista[["MAD"]] <- NULL
  resInd <- sapply(lista, "[[", 5)
  resInd <- sort(resInd)
  resInd[names(resInd)] <- 1:8
  mapeRealRank[[nombre]] <- resInd # Real classification
}

# normScore rank order by real accuracy order
normScoreRank <- list()
for (nombre in names(resNormScore)){
  # orden real por MAPE
  realOrden <- names(mapeRealRank[[nombre]])
  
  # Orden por normScore
  resInd <- resNormScore[[nombre]]
  resInd <- sort(resInd)
  resInd[names(resInd)] <- 1:8
  
  # Ordenar según ranking real
  resInd <- resInd[realOrden]
  
  # Out
  normScoreRank[[nombre]] <- resInd
}


# Kendall correlation
corRes <- sapply(names(mapeRealRank), function(i) cor(
  x = unname(mapeRealRank[[i]]), 
  y = unname(normScoreRank[[i]]),
  method = "kendall"), USE.NAMES = T, simplify = F)
```

```{r}
# preparing data
resNormScoreNames <- lapply(resNormScore, names)
mapeRealRankNames <- lapply(mapeRealRank, names)


### Global ####
# Non corrected
summaryGlobal <- resultsGlobal(
  resGlobalNS = resNormScoreNames, 
  resGlobalGS_BEST = lapply(mapeRealRankNames, function(i) i[1]),
  resGlobalGS_BESTS = lapply(mapeRealRankNames, function(i) i[1:3]), 
  resGlobalGS_WORST = NULL
  )
```

### Best methods (top) {.tabset}

#### Top 1 - only the best method {-}

```{r}
summaryGlobal$Best$hitTable
```

#### Top 1 - all best methods {-}

```{r}
summaryGlobal$Bests$hitTable
```


#### MRR - only the best method {-}

```{r}
# allClassess <- rev(sort(unique(df$Pos)))
allClassess <- 1/1:8
df <- data.frame(Pos = summaryGlobal$Best$mrrRes)
df$Position <- factor(
  df$Pos, 
  levels = allClassess, 
  # levels = rev(sort(unique(df$Pos))), 
  labels = paste0("Posición ", 1:8))
Biostatech::getCatTable(df$Position)$tablaFormato
```

#### MRR - all best methods {-}

```{r}
df <- data.frame(Pos = summaryGlobal$Bests$mrrRes)
df$Position <- factor(
  df$Pos, 
  levels = allClassess, 
  labels = paste0("Posición ", 1:8))
Biostatech::getCatTable(df$Position)$tablaFormato
```

#### MRR bottom - all best methods {-}

La posición más baja de la mejor normalización del grupo determinado por MAPE.  

```{r}
df <- data.frame(Pos = summaryGlobal$Bests$mrrResBottom)
df$Position <- factor(
  df$Pos, 
  levels = allClassess, 
  labels = paste0("Posición ", 1:8))
Biostatech::getCatTable(df$Position)$tablaFormato
```
