---
title: "Evaluation of MaxQuant performance in a HPC enviroment"
subtitle: "Executions in Finis Terrae III (CESGA)"
author:
- name: "Julia García Currás"
  affiliation: "julia.gcurras@biostatech.com"
date: "`r Sys.setlocale('LC_TIME', 'English'); format(Sys.Date(), '%d  %B  %Y')`"

output: 

  bookdown::html_document2:
    toc: true    # tabla de contenidos
    toc_depth: 4 # depth of headers (4 --> todos los niveles incluidos)
    toc_float: true
    number_sections: true
    self_contained: yes
    css: ./Complementos/Biostatech_long_tittle.css
    theme: flatly
    highlight: pygments
    fig_caption: true
    includes:
      in_header: "./Complementos/favicon.html"
      after_body: ./Complementos/footer.html
---

<img src="./Complementos/logolong.svg" style="position:absolute;top:0.5px;right:0px;width:250px;height:130px;" />

<style>
.tabset-dropdown > .nav-tabs {
    display: inline-block;
    max-height: 400px;
    min-height: 50px;
    overflow-y: auto;
    background: white;
    border: 1px solid #ddd;
    border-radius: 4px;
}
</style>


```{r chunk_setup, include=FALSE}

knitr::opts_chunk$set(
  eval = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  include = TRUE,
  results = 'asis', 
  fig.align='center', 
  fig.height=5, 
  # fig.width=8
)

```

```{r librerias y otros, include=FALSE, warning=FALSE}

#--- Clear existing data and graphics
rm(list=ls())
graphics.off()
#--- Set CRAN Repo
options(repos = c(CRAN = "https://cloud.r-project.org"))
#--- Loading required libraries
library(lubripack)
list.of.packages <- c("dplyr","arsenal", "ggplot2", "knitr", 'DT', 
                      "plotly", "ggpubr", "httr", "glue",
                      "usethis", "glossary", "yaml")
suppressMessages(suppressPackageStartupMessages(lubripack(list.of.packages, silent = TRUE)))

library(Biostatech)
#--- Mensaje de status
if(all(sapply(list.of.packages, require, character.only = TRUE))) message("Librerías cargadas correctamente.") else message("(!) Hay algún problema con las librerías necesarias.")
#--- Session information
writeLines(capture.output(sessionInfo()), "sessionInfo.txt")
options(qwraps2_markup = "markdown")


js <- c(
"function(row, data, num, index){",
"  var $row = $(row);",
"  if($row.hasClass('even')){",
"    $row.css('background-color', 'white');",
"    $row.hover(function(){",
"      $(this).css('background-color', 'lightgrey');",
"     }, function(){",
"      $(this).css('background-color', 'white');",
"     }",
"    );",  
"  }else{",
"    $row.css('background-color', '#EDFDFA');",
"    $row.hover(function(){",
"      $(this).css('background-color', 'lightgrey');",
"     }, function(){",
"      $(this).css('background-color', '#EDFDFA');",
"     }",
"    );",  
"  }",
"}"  
)
# 
# DT::datatable(dfFinal, extensions = "Buttons", 
#     rownames = T, escape = F, class = c("hover", "row-border"), 
#     options = list(ordering = T, dom = "Brt", scrollY ='500px', 
#                    rowCallback = DT::JS(js), full_width = T, 
#                    scrollX = TRUE, pageLength = nrow(dfFinal),
#                    buttons = c("copy", "csv", "excel"))) %>%
#   DT::formatRound(1:ncol(dfFinal), digits = 3)

```

```{r}

plotlyScatter <- function(df, xVar = "TotalThreads", yVar = "Time (s)",
                          groupVar = NULL, 
                          tituloX = NULL, tituloY = NULL, 
                          tituloLeyenda = "Total threads",
                          colores = "#005B9A", yLim = NULL){
  
  if (is.null(tituloX)) tituloX <- xVar
  if (is.null(tituloY)) tituloY <- yVar
  if (is.null(yLim)) yLim <- max(df[, yVar], na.rm = TRUE) * 1.05
  
  if (is.null(groupVar)){
    df <- df[,c(xVar, yVar)]
    colnames(df) <- c("varX", "varY")
    
    plot_ly(
      df,
      x = ~varX,
      y = ~varY,
      type = "scatter",
      mode = "lines+markers",
      line = list(width = 2, color = colores),
      marker = list(size = 7, color = colores), 
      text = paste0(
                tituloX, ": ", df$varX,
                "<br>", tituloY, ": ", df$varY
              ),
      hoverinfo = 'text'
      ) %>%
      layout(
        xaxis = list(title = tituloX),
        yaxis = list(title = tituloY, range = c(0, yLim))
      ) %>%
      plotly::config(
              modeBarButtonsToRemove = c(
                "autoScale2d", "lasso2d", "pan2d",
                "select2d"),
              displaylogo = FALSE
    )
    
    
  } else {
    d <- df[, c(xVar, yVar, groupVar)]
    colnames(d) <- c("varX", "varY", "grupo")
  
    # Asegurar 2 grupos
    d$grupo <- as.factor(d$grupo)
    lev <- levels(d$grupo)
    
    if (length(colores)!=length(lev)) colores <- Biostatech::colorPalette(n = length(lev))
    col_map <- setNames(rep(colores, length.out = 2), lev)
  
    # Orden: para que las líneas no salten, ordenamos por grupo y X
    d <- d[order(d$grupo, d$varX), ]
  
    # Colores por nivel (en orden de levels)
  
    plotly::plot_ly(
      data = d,
      x = ~varX,
      y = ~varY,
      type = "scatter",
      mode = "lines+markers",
      color = ~grupo,
      colors = col_map,
      split = ~grupo,  # una traza por grupo
      line = list(width = 2),
      marker = list(size = 7),
      text = ~paste0(
        "Group: ", grupo,
        "<br>", tituloX, ": ", varX,
        "<br>", tituloY, ": ", varY
      ),
      hoverinfo = "text"
    ) %>%
      plotly::layout(
        xaxis = list(title = tituloX, range = c(0, 9)),
        yaxis = list(title = tituloY, range = c(0, yLim)),
        legend = list(title = list(text = tituloLeyenda))
      ) %>%
      plotly::config(
        modeBarButtonsToRemove = c("autoScale2d", "lasso2d", "pan2d", "select2d"),
        displaylogo = FALSE
      )
    }
}



```




# Main objective

Determine the best parameters of execution for normScore simulations in a High Performance Computing (HPC) enviroment in terms of memory and threads. 


# Methods

## Computational parameters

Execution was performed in the Finis Terrae III (FTIII) supercomputer from the [Centro de Supercomputación de Galicia (CESGA)](https://www.cesga.es/gl/inicio-gl/). The FTIII was accessed remotely using a ssh client and a VPN connection through Check point mobile app. Data transfer was done both using the command line (through scp client) and the [WINscp transfer file tool](https://winscp.net/eng/download.php).

## Data

The following data was collected for each dataset execution with an specific number of threads:

* Time of execution

* Total memory used

Using the previous information, the following parameters were estimated:

* $\text{Memory per thread} = \frac{\text{total memory (GB)}}{\text{nº threads}}$

* $\text{Speed up} = \frac{\text{sequential time}}{\text{parallel time}}$

* $\text{Efficiency}= \frac{\text{Speed up}}{\text{nº of threads}}$

Some definitions:

* Sequential time: time without parallelization (1 thread). 

* Parallel time: time of execution using a given number of threads.

* Speed up: comparison of sequential time with parallel time, measures the real reduction in time achieved with the parallelization. 

* Efficiency: time fraction of useful work for each nuclei. 

# Results

## Main results {.tabset}

Increasing number of threads.

```{r}
data <- readRDS(file = "../OutputFiles/data.rds")
dfPrin <- data[[1]]
dfSec <- data[[2]]
```

```{r}
df <- dfPrin %>% dplyr::select(TotalThreads, Cores:Nodes, `Memory Utilized (GB)`, `Memory By Thread (GB)`, `Time (s)`, `Time (min)`, SpeedUp, Efficiency)
DT::datatable(df, extensions = "Buttons",
    rownames = F, escape = F, class = c("hover", "row-border"),
    options = list(ordering = T, dom = "Brt", scrollY =F,
                   rowCallback = DT::JS(js), full_width = T,
                   scrollX = TRUE, pageLength = nrow(df),
                   buttons = c("copy", "csv", "excel"))) %>%
  DT::formatRound(5:ncol(df), digits = 2) %>%
  DT::formatStyle(1, fontWeight = 'bold')

```

### Execution time (seconds) {-}

```{r fig.align='center', fig.height=5, fig.width=8}
plotlyScatter(df = dfPrin, colores = Biostatech::colorPalette(n=3)[1])
```

### Speed up {-}

```{r}
plotlyScatter(df = dfPrin, yVar = "SpeedUp", 
              tituloX = "Total threads",
              colores = Biostatech::colorPalette(n=3)[2])
```


### Efficiency {-}

```{r}
plotlyScatter(df = dfPrin, yVar = "Efficiency", 
              tituloX = "Total threads",
              colores = Biostatech::colorPalette(n=3)[3])
```


### Total memory {-}

```{r}
plotlyScatter(df = dfPrin, yVar = "Memory Utilized (GB)", 
              tituloX = "Total threads",
              colores = "#C67DD8")
```

### Memory/thread {-}

```{r}
plotlyScatter(df = dfPrin, yVar = "Memory By Thread (GB)", 
              tituloX = "Total threads",
              colores = "#9389C7")
```


## Secondary results {.tabset}

Increasing cores and threads. 


```{r}
df <- dfSec %>% dplyr::select( ThreadGroup, TotalThreads, Cores:Nodes, `Memory Utilized (GB)`, `Memory By Thread (GB)`, `Time (s)`, `Time (min)`, SpeedUp, Efficiency)
DT::datatable(df, extensions = "Buttons",
    rownames = F, escape = F, class = c("hover", "row-border"),
    options = list(ordering = T, dom = "Brt", scrollY =F,
                   rowCallback = DT::JS(js), full_width = T,
                   scrollX = TRUE, pageLength = nrow(df),
                   buttons = c("copy", "csv", "excel"))) %>%
  DT::formatRound(5:ncol(df), digits = 2) %>%
  DT::formatStyle(1, fontWeight = 'bold')

```


### Execution time (seconds) {-}

```{r fig.align='center', fig.height=5, fig.width=8}
plotlyScatter(df = dfSec, groupVar = "ThreadGroup", xVar = "Cores")
```

### Speed up {-}

```{r}
plotlyScatter(df = dfSec, groupVar = "ThreadGroup", 
              xVar = "Cores", yVar = "SpeedUp")
```


### Efficiency {-}

```{r}
plotlyScatter(df = dfSec, groupVar = "ThreadGroup", 
              xVar = "Cores", yVar = "Efficiency")
```

### Total memory {-}

```{r}
plotlyScatter(df = dfSec, groupVar = "ThreadGroup", 
              xVar = "Cores",  yVar = "Memory Utilized (GB)")
```

### Memory/thread {-}

```{r}
plotlyScatter(df = dfSec, groupVar = "ThreadGroup", 
              xVar = "Cores", yVar = "Memory By Thread (GB)")
```
