---
title: "NormScore assessment - Simulation results"
subtitle: "Executions in Finis Terrae III (CESGA)"
author:
- name: "Julia García Currás"
  affiliation: "julia.gcurras@biostatech.com"
date: "`r Sys.setlocale('LC_TIME', 'English'); format(Sys.Date(), '%d  %B  %Y')`"

output: 

  bookdown::html_document2:
    toc: true    # tabla de contenidos
    toc_depth: 4 # depth of headers (4 --> todos los niveles incluidos)
    toc_float: true
    number_sections: true
    self_contained: yes
    css: ./Complementos/Biostatech_long_tittle.css
    theme: flatly
    highlight: pygments
    fig_caption: true
    includes:
      in_header: "./Complementos/favicon.html"
      after_body: ./Complementos/footer.html
---

<img src="./Complementos/logolong.svg" style="position:absolute;top:0.5px;right:0px;width:250px;height:130px;" />

<style>
.tabset-dropdown > .nav-tabs {
    display: inline-block;
    max-height: 400px;
    min-height: 50px;
    overflow-y: auto;
    background: white;
    border: 1px solid #ddd;
    border-radius: 4px;
}
</style>


```{r chunk_setup, include=FALSE}

knitr::opts_chunk$set(
  eval = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  include = TRUE,
  results = 'asis', 
  fig.align='center', 
  fig.height=5
  # fig.width=8
)

```

```{r librerias y otros, include=FALSE, warning=FALSE}

#--- Clear existing data and graphics
rm(list=ls())
graphics.off()
#--- Set CRAN Repo
options(repos = c(CRAN = "https://cloud.r-project.org"))
#--- Loading required libraries
library(lubripack)
list.of.packages <- c("dplyr","arsenal", "ggplot2", "knitr", 'DT', 
                      "plotly", "ggpubr", "Biostatech")
suppressMessages(suppressPackageStartupMessages(lubripack(list.of.packages, silent = TRUE)))

library(Biostatech)
#--- Mensaje de status
if(all(sapply(list.of.packages, require, character.only = TRUE))) message("Librerías cargadas correctamente.") else message("(!) Hay algún problema con las librerías necesarias.")
#--- Session information
writeLines(capture.output(sessionInfo()), "sessionInfo.txt")
options(qwraps2_markup = "markdown")


js <- c(
"function(row, data, num, index){",
"  var $row = $(row);",
"  if($row.hasClass('even')){",
"    $row.css('background-color', 'white');",
"    $row.hover(function(){",
"      $(this).css('background-color', 'lightgrey');",
"     }, function(){",
"      $(this).css('background-color', 'white');",
"     }",
"    );",  
"  }else{",
"    $row.css('background-color', '#EDFDFA');",
"    $row.hover(function(){",
"      $(this).css('background-color', 'lightgrey');",
"     }, function(){",
"      $(this).css('background-color', '#EDFDFA');",
"     }",
"    );",  
"  }",
"}"  
)

df <- readRDS(file = "../allSimulations.rds")
df <- df %>% filter(!(especificos %in% c(1,8)))

# df <- df %>% filter(especificos %in% c(0, 4, 5, 6, 7))
```

# Simulations

A first evaluation of the normScore was performed using simulation datasets. 

Description:

* Nine different datasets were simulated with an increasing error for each item or group of items.

* The previous combination of 9 datasets was repeated several times changing the following parameters: 
  
  * Magnitude of error: 0 (no error), 1-8 (increased error). 
  * Number of proteins: 100, 1000, 5000, 10000.
  * Number of samples per group: 5, 10, 20, 50.

* These simulations were also repeated 20 times using different seeds. 

A total number of `r nrow(df)` combinations of the previous parameters were used to simulate each time 9 different datasets, which means a total number of `r (2880*9)` simulated datasets. 

In addtition, five different errors were necessary to assess all items:

* Item 0, 1, 5 and 6: shift error
* Item 2: correlation between/within magnitude
* Item 3: shift+residual variance
* Item 4: mean-SD dependence
* normScore: a general combination of shift error, correlation magnitude, residual variance magnitude and dependence of mean-SD

For each of the previous items `r (2880*9)` simulated datasets were generated, different combinations for the error. Therefore, the final number of simulations was `r (2880*9*5)`.

For each combination of parameters (magnitude of error, no. proteins, no. samples/group, repetition), the item/normScore was used to assess the 9 simulated datasets. The resulting order was compared with the expected one (datasets 0 to 8 sorted from higher to lower quality) using the Kendall correlation coefficient. A total number of `r (2880*5)` Kendall correlation coefficients was obtained and used in this report to assess the performance of each item and the global score. 


# Results

## By item

```{r}
df2 <- df %>%
  tidyr::pivot_longer(
    cols = c(starts_with("Item"), "normScore"),
    names_to = "Items",
    values_to = "corr"
  ) %>%
  tidyr::pivot_wider(
    names_from = especificos,
    values_from = corr
  )
dfAux <- df2 %>% dplyr::select(Items, `0`:`7`)
colnames(dfAux)[-1] <- paste0("Type of error (", colnames(dfAux)[-1], ")")
Biostatech::tableDescr(Items ~ ., data = dfAux, onlyDescr = T)$tablaFormato
```


```{r}
colores <- Biostatech::colorPalette(n = length(unique(df$especificos)))
names(colores) <- unique(df$especificos)
graficos <- sapply(unique(df$especificos), function(i){
  dfAux <- df %>% filter(especificos == i) %>% dplyr::select(Item0:normScore)
  Biomics::plotBoxMulti(
    base = dfAux, varResumen = colnames(dfAux), titulo = paste0("Error ", i), 
    interact = F, 
    color = rep(unname(colores[as.character(i)]), 8))$grafico + ylim(c(-1, 1))
})
```

```{r  fig.height=12, fig.align='center', fig.width=10}
ggpubr::ggarrange(plotlist = graficos, nrow = 3, ncol = 3) 
```



## By nº. proteins

```{r}
df2 <- df %>%
  tidyr::pivot_longer(
    cols = c(starts_with("Item"), "normScore"),
    names_to = "Items",
    values_to = "corr"
  ) %>%
  tidyr::pivot_wider(
    names_from = n_proteins,
    values_from = corr
  )
dfAux <- df2 %>% dplyr::select(Items, `100`:`10000`)
colnames(dfAux)[-1] <- paste0("Nº proteins:", colnames(dfAux)[-1])
Biostatech::tableDescr(Items ~ ., data = dfAux, onlyDescr = T)$tablaFormato
```


```{r}
colores <- Biostatech::colorPalette(n = 4)
names(colores) <- unique(df$n_proteins)
graficos <- sapply(unique(df$n_proteins), function(i){
  dfAux <- df %>% 
    filter(n_proteins == i) %>% 
    filter(especificos != 0) %>% # control negativo
    mutate(Item3 = if_else(especificos == 1, NA, Item3)) %>% # control negativo
    dplyr::select(Item0:normScore)
  Biomics::plotBoxMulti(
    base = dfAux, varResumen = colnames(dfAux), titulo = paste0("Nº proteins:  ", i), 
    interact = F, color = rep(unname(colores[as.character(i)]), 8))$grafico + ylim(c(-1, 1))
})
```

```{r  fig.height=8, fig.align='center', fig.width=10}
ggpubr::ggarrange(plotlist = graficos, nrow = 2, ncol = 2)
```



## By nº. samples/group


```{r}
df2 <- df %>%
  tidyr::pivot_longer(
    cols = c(starts_with("Item"), "normScore"),
    names_to = "Items",
    values_to = "corr"
  ) %>%
  tidyr::pivot_wider(
    names_from = n_per_group,
    values_from = corr
  )
dfAux <- df2 %>% dplyr::select(Items, `5`:`50`)
colnames(dfAux)[-1] <- paste0("Nº samples/group: ", colnames(dfAux)[-1])
Biostatech::tableDescr(Items ~ ., data = dfAux, onlyDescr = T)$tablaFormato
```

```{r}
colores <- Biostatech::colorPalette(n = 4)
names(colores) <- unique(df$n_per_group)
graficos <- sapply(unique(df$n_per_group), function(i){
  dfAux <- df %>% 
    filter(n_per_group == i) %>% 
    filter(especificos != 0) %>% # control negativo
    mutate(Item3 = if_else(especificos == 1, NA, Item3)) %>% # control negativo
    dplyr::select(Item0:normScore)
  Biomics::plotBoxMulti(
    base = dfAux, varResumen = colnames(dfAux), titulo = paste0("Nº samples:  ", i), 
    interact = F, 
    color = rep(unname(colores[as.character(i)]), 8))$grafico + ylim(c(-1, 1))
})
```

```{r fig.height=8, fig.align='center', fig.width=10}
ggpubr::ggarrange(plotlist = graficos, nrow = 2, ncol = 2)
```




## By nº. samples/group

```{r}
df2 <- df %>%
  tidyr::pivot_longer(
    cols = c(starts_with("Item"), "normScore"),
    names_to = "Items",
    values_to = "corr"
  ) %>%
  tidyr::pivot_wider(
    names_from = semilla,
    values_from = corr
  )
dfAux <- df2 %>% dplyr::select(Items, `107`:`11792`)
colnames(dfAux)[-1] <- paste0("Nº samples/group: ", colnames(dfAux)[-1])
Biostatech::tableDescr(Items ~ ., data = dfAux, onlyDescr = T)$tablaFormato
```


```{r}
colores <- Biostatech::colorPalette(n = 20, removeWhite = T)
names(colores) <- unique(df$semilla)
graficos <- sapply(unique(df$semilla), function(i){
  dfAux <- df %>% 
    filter(semilla == i) %>% 
    filter(especificos != 0) %>% # control negativo
    mutate(Item3 = if_else(especificos == 1, NA, Item3)) %>% # control negativo
    dplyr::select(Item0:normScore)
  Biomics::plotBoxMulti(
    base = dfAux, varResumen = colnames(dfAux), titulo = paste0("Repetición (semilla):  ", i), 
    interact = F, color = rep(unname(colores[as.character(i)]), 8))$grafico + ylim(c(-1, 1))
})
```

```{r fig.height=20, fig.align='center', fig.width=10}
ggpubr::ggarrange(plotlist = graficos, nrow = 10, ncol = 2)
```



# Summary

Even though we can see outliers in some items, specially at item3 and item5, median and Q1-Q3 values are higher than 0.9 in general. 

Items and normScore are invaried to the number of proteins and numbre of samples by group. No extrem seed was stablish, data behaviour ir similar across the 20 seeds used. 

General performance of normScore is slightly lower in terms of median, but with almost no extreme or outlier correlation values and thin IQR values. 

_Especificos_ 1 and 8 combinations correspond to extrem conditions and were be removed for reporting the final results. 



